Lens Modeling in \sw

### 2014-04-02 text/ms.tex
changed to mn2e format

\documentclass[12pt,preprint]{aastex}

@@

%\usepackage{longtable}   % those two to generate the 2 ol table
%\usepackage{multicol}

@@

\title{Lens Modeling in \sw}
\author{First Author,\altaffilmark{1}
Second Author,\altaffilmark{2} and
Third Author\altaffilmark{3}}
\altaffiltext{1}{First place}
\altaffiltext{2}{Second place}
\altaffiltext{3}{Third place}

\begin{abstract}
In the initial phase of \sw (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses.
Here we report on a web application that gives experienced volunteers the opportunity to model the candidates that have been identified.
In order to gauge the quality of the models that were being rendered, these same volunteers were invited to model a sample of 29 simulated lenses.
The models were then examined in greater detail, with particular attention being paid to the following:
(i)~identification of image parities and time arrivals;
(ii)~the mean convergence (equivalent to the enclosed mass), and finally;
(iii)~the performance of a volunteer vs. a professional.
In most cases, the volunteers were found to correctly identify the image parities and time arrivals.
% Einstein radius +~20%
 along with a mean convergence that was well constrained within the image region;
In all, the results could be comparable to that of a professional.

\end{abstract}

\keywords{}
\section{Introduction}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 423 published lenses considered secure as
  of January 2014 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

\bibliographystyle{apj}
\bibliography{bib/ms}

>>>>

\documentclass[usenatbib,onecolumn]{mn2e}

@@

\newcommand{\apj}{ApJ}
\newcommand{\apjs}{ApJS}
\newcommand{\apjl}{ApJL}
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\mnras}{MNRAS}
\newcommand{\aj}{AJ}
\newcommand{\araa}{ARAA}
\newcommand{\pasp}{PASP}
\newcommand{\pasj}{PASJ}

@@

\title{Lens Modeling in \sw}

\author[Kueng et al]{Rafael Kueng,$^{1}$
Phil Marshall,$^{2}$
Anupreeta More,$^{3}$
Aprajita Verma,$^{4}$
Amit Kapadia,$^{5}$
\newauthor
Elisabeth Baeten,$^{6}$
Claude Cornen,$^{6}$
Christine McMillan,$^{6}$
Julianne Wilcox,$^{6}$
\newauthor
Jonas Odermatt,$^{7}$
Jonathan Coles,$^{8}$
Surhud More$^{3}$
and Prasenjit Saha$^{1}$ \\
$^{1}$Physik-Institut, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
$^{3}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
$^{4}$Oxford Astrophysics, Keble Road, Oxford OX1 3RH, UK\\
$^{5}$Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA\\
$^{6}$Spacewarps\\
$^{7}$Kantonsschule Zug, L\"ussiweg 24, 6300 Zug, Switzerland\\
$^{8}$Exascale Computing Lab, Versailles Saint-Quentin-en-Yveline University, 55 Avenue des Etats Unis, 78000, Versailles, France}

\maketitle

\begin{abstract}
In the initial phase of \sw (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses.
Here we report on a web application that gives experienced volunteers the opportunity to model the candidates that have been identified.
In order to gauge the quality of the models that were being rendered, these same volunteers were invited to model a sample of 29 simulated lenses.
The models were then examined in greater detail, with particular attention being paid to the following:
(i)~identification of image parities and time arrivals;
(ii)~the mean convergence (equivalent to the enclosed mass), and finally;
(iii)~the performance of a volunteer vs. a professional.
In most cases, the volunteers were found to correctly identify the image parities and time arrivals.
% Einstein radius +~20%
 along with a mean convergence that was well constrained within the image region;
In all, the results could be comparable to that of a professional.
\end{abstract}

\begin{keywords}
\end{keywords}

\section{Introduction}

@@

\begin{figure}
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 423 published lenses considered secure as
  of January 2014 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

\bibliographystyle{mn2e}
\bibliography{bib/ms}
